### 2014-07-22 MS.tex
sections and subsections

\begin{document}
% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf{Diversity dynamics in Nymphalidae butterflies: Effect of
phylogenetic uncertainty on diversification rate shift estimates}
}
% Insert Author names, affiliations and corresponding author email.
\\
Carlos Pe\~na$^{1,\ast}$, 
Marianne Espeland$^{2}$
\\
\bf{1} Carlos Pe\~na Laboratory of Genetics, Department of Biology, University of Turku, Turku
\\
\bf{2} Museum of Comparative Zoology and Department of Organismic and
Evolutionary Biology, Harvard University, Cambridge, USA. Email:
\href{mailto:marianne.espeland@gmail.com}{marianne.espeland@gmail.com}.
Current address: McGuire Center for Lepidoptera and Biodiversity,
Florida Museum of Natural History, University of Florida, Gainesville,
FL, US
\\
$\ast$ E-mail: Corresponding mycalesis@gmail.com
\end{flushleft}

\subsection{Abstract}\label{abstract}

@@

\subsection{Introduction}\label{introduction}

@@

\subsection{Methods}\label{methods}

\subsubsection{Data}\label{data}

@@

\subsubsection{Analyses of
Diversification}\label{analyses-of-diversification}

@@

\subsubsection{Detecting diversification shifts on phylogenetic
trees}\label{detecting-diversification-shifts-on-phylogenetic-trees}

@@

\subsubsection{Estimation of trait-dependent speciation
rates}\label{estimation-of-trait-dependent-speciation-rates}

@@

\subsection{Results}\label{results}

\subsubsection{Detecting diversification shifts on the maximum clade
credibility
tree}\label{detecting-diversification-shifts-on-the-maximum-clade-credibility-tree}

@@

\subsubsection{Phylogenetic uncertainty in the MultiMEDUSA
approach}\label{phylogenetic-uncertainty-in-the-multimedusa-approach}

@@

\subsubsection{Estimation of trait-dependent speciation
rates}\label{estimation-of-trait-dependent-speciation-rates-1}

@@

\subsection{Discussion}\label{discussion}

\subsubsection{Effects of phylogenetic uncertainty on the performance of
MEDUSA}\label{effects-of-phylogenetic-uncertainty-on-the-performance-of-medusa}

@@

\subsubsection{Hostplant use and diversification in
Nymphalidae}\label{hostplant-use-and-diversification-in-nymphalidae}

\paragraph{Ithomiini}\label{ithomiini}

@@

\paragraph{Danaini}\label{danaini}

@@

\paragraph{\emph{Charaxes}}\label{charaxes}

@@

\paragraph{Satyrini}\label{satyrini}

@@

\subsection{Acknowledgments}\label{acknowledgments}

@@

\subsection{Figure legends}\label{figure-legends}

@@

\subsection{Tables}\label{tables}

@@

\section{Supp. mat.}\label{supp.-mat.}

@@

\subsection{References}\label{references}

>>>>

\begin{document}
% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf{Diversity dynamics in Nymphalidae butterflies: Effect of
phylogenetic uncertainty on diversification rate shift estimates}
}
% Insert Author names, affiliations and corresponding author email.
\\
Carlos Pe\~na$^{1,\ast}$, 
Marianne Espeland$^{2}$
\\
\bf{1} Carlos Pe\~na Laboratory of Genetics, Department of Biology, University of Turku, Turku
\\
\bf{2} Museum of Comparative Zoology and Department of Organismic and
Evolutionary Biology, Harvard University, Cambridge, USA. Email:
marianne.espeland@gmail.com.
Current address: McGuire Center for Lepidoptera and Biodiversity,
Florida Museum of Natural History, University of Florida, Gainesville,
FL, US
\\
$\ast$ E-mail: Corresponding mycalesis@gmail.com
\end{flushleft}

\section*{Abstract}

@@

\section*{Introduction}

@@

\section*{Materials and Methods}

\subsection*{Data}

@@

\subsection*{Analyses of Diversification}

@@

\subsection*{Detecting diversification shifts on phylogenetic trees}

@@

\subsection*{Estimation of trait-dependent speciation rates}

@@

\section*{Results}

\subsection*{Detecting diversification shifts on the maximum clade credibility tree}

@@

\subsection*{Phylogenetic uncertainty in the MultiMEDUSA approach}

@@

\subsection*{Estimation of trait-dependent speciation rates}

@@

\section*{Discussion}

\subsection*{Effects of phylogenetic uncertainty on the performance of MEDUSA}

@@

\subsection*{Hostplant use and diversification in Nymphalidae}

\subsubsection*{Ithomiini}

@@

\subsubsection*{Danaini}

@@

\subsubsection*{\emph{Charaxes}}

@@

\subsubsection*{Satyrini}

@@

\section*{Acknowledgments}

@@

\section*{Figure legends}

@@

\section*{Tables}

@@

\section*{Supp. mat.}

@@

\section*{References}
